% ============================================================
\section{Introduction}
\label{sec:introduction}

\subsection{Capital Returns: From Equities to Tokens}

Modern public equities have evolved a disciplined vocabulary for returning capital to holders. Dividend policy, open-market share repurchases, special distributions, and the legal apparatus of par-value redemption together constitute a century of accumulated institutional design \citep{GrullonMichaely2002,Skinner2008}. Each instrument resolves a different commitment problem: dividends signal earnings persistence at the cost of inflexibility; buybacks substitute for dividends with greater discretion but a weaker commitment \citep{IkenberryLakonishokVermaelen1995}; retractable bonds give the holder an exit at par price but at the cost of issuer optionality \citep{BrennanSchwartz1977}; and closed-end mutual funds promise net asset value (NAV) but do not enforce it on the secondary market, generating a persistent discount that has resisted decades of theoretical attention \citep{LeeShleiferThaler1991,Pontiff1996,CherkesSagiStanton2009}.

Tokens issued on programmable blockchains inherit none of this institutional infrastructure by default. A token's supply, its claim on cash flows, and the conditions under which a holder can exit are whatever the issuing contract says they are. The historical record is unkind. Tokens marketed as ``backed'' have been backed by promises rather than redeemable claims; ``floor prices'' have been rhetorical descriptions of treasury-to-supply ratios rather than enforceable contracts; treasuries advertised as protocol-owned have been emptied by governance votes; and reserve currencies have spiraled into reflexive collapse under coordinated pressure \citep{LiuMakarovSchoar2023,KlagesMundtMinca2021}. The pattern is consistent: the language of TradFi capital returns has been used without the underlying enforcement primitives that made those returns credible in the first place.

This paper takes the inverse view. We ask: what is the simplest on-chain primitive that delivers a capital-return commitment with the same enforcement discipline that TradFi instruments achieve through securities law, board fiduciary duty, and corporate-governance structures---but expressed entirely as smart-contract invariants? We give an answer, and prove it.

\subsection{Monotonic Math}

We present \emph{Monotonic Math} (henceforth M\textsuperscript{2}), a tokenomic primitive composed of four immutable contracts: a fixed-supply ERC-20 token with a redeem function, a passive stablecoin treasury with no admin withdraw path, an asymmetric-fee automated market maker (AMM) implemented as a Uniswap v4 hook \citep{UniswapV4}, and a revenue router with a hardcoded split. The protocol is deployed once, accepts business revenue in a backing stablecoin, and operates without governance, upgrade, or parameter-change paths.

The mechanism's load-bearing property is what we call \emph{floor monotonicity}: under every operation that the protocol permits---revenue deposit, buy-and-burn, redemption, transfer, liquidity-pool swap (in either direction), and fee collection---the per-token redeemable claim on the treasury, $\Floor = \Tres / \Sup$, is non-decreasing. We prove this by case analysis over the protocol's operation set (Section~\ref{sec:formal-invariants}). The property is structural rather than empirical: it does not depend on market behavior, holder coordination, or operator discretion. It depends on the contract code and on the backing stablecoin remaining solvent.

Two consequences distinguish M\textsuperscript{2} from prior on-chain primitives that have used the language of floors and redemptions. First, holders have two exit paths---redeem at the contractual floor or sell to the AMM---and \emph{neither is floor-negative}. Redemption preserves the floor exactly (Case~3); selling to the AMM applies a Pigovian fee that, on subsequent realization, raises the floor (Cases~5 and~7). There is no protocol-defined operation that lowers the floor. Second, the asymmetric AMM fee (0.10\% on buys, 3.00\% on sells, with the sell fee accruing as protocol-realizable fee growth) routes adversarial pressure into common-pool value: an attempted bank run against the AMM raises the floor for those who do not run.

The mechanism is best understood, in TradFi vocabulary, as the \emph{composition} of three instruments that do not coexist in any single offering: a closed-end fund with continuous NAV-redemption (so the secondary-market discount is mathematically pinned at zero), a sponsor-funded perpetual buyback program with no announcement-execution gap (so capital returns are deterministic from earnings), and a Pigovian sell tax recycled into common-pool value rather than to a third-party fisc. No existing TradFi instrument we are aware of binds these three together---not because they could not be combined in principle, but because the contract-as-trust substrate that enforces their irrevocable composition is absent in conventional securities law.

\subsection{Contributions}

We make three contributions, stated precisely so that what we claim is separated from what we do not.

\textbf{C1 (Primitive).} We specify M\textsuperscript{2} as a complete, deployable protocol with four immutable contracts and quantify its design space through four free parameters: revenue rate, liquidity-pool seed fraction, asymmetric fee asymmetry, and treasury seed. We identify the genesis constraint $\Tres_0 / \Sup_0 = L_{s,0} / L_{t,0}$ under which floor and spot coincide at launch, and characterize the protocol's terminal state under deterministic buy-and-burn (the liquidity-pool half-life is $L_{s,0}/B$, where $B$ is the monthly buy-and-burn size).

\textbf{C2 (Proofs).} Three results form the headline of our formal contribution. First, \emph{floor monotonicity} (Theorem~\ref{thm:floor-monotonicity}): under every operation in the protocol's complete operation set, the per-token redemption floor $\Floor = \Tres/\Sup$ is non-decreasing; the proof is by case analysis over the operation set, sharpened by an integer-arithmetic refinement showing that on-chain truncation residuals accumulate strictly in the treasury's favor (Lemma~\ref{lem:integer-redemption}). Second, a \emph{composite-strategy bank-run theorem} (Theorem~\ref{thm:bank-run}): within the class of \emph{simultaneous} attacker strategies---those in which the attacker's LP dump and treasury redemption occur in a single block without an intervening \texttt{collectFees} realization---the optimal dump quantity saturates at a closed-form quantity $A^*$ that depends only on the AMM state and the floor, not on the attacker's holdings $N$; the attacker's profit premium over pure redemption is then a state-only constant $\Delta^*$, and the marginal value per held token converges to the floor as $N \to \infty$. Third, \emph{redemption fairness} (Theorem~\ref{thm:redemption-fairness}): under the operations available to a holder, the per-token payout of a later redeemer weakly dominates that of an earlier redeemer, structurally inverting the open-end mutual-fund first-mover advantage of \citet{ChenGoldsteinJiang2010} that underlies classical Diamond--Dybvig run dynamics \citep{DiamondDybvig1983}.
Auxiliary results bound LP exhaustion (Theorem~\ref{thm:lp-half-life}), the calling equilibrium for permissionless fee collection (Theorem~\ref{thm:collect-equilibrium}), MEV leakage under the protocol's mitigations (Theorem~\ref{thm:mev-bound}), and spot--floor convergence under operator-revenue cessation (Theorem~\ref{thm:spot-floor-convergence}); a directional inversion of the Loss-Versus-Rebalancing identity of \citet{MilionisMoallemiRoughgarden2023} is stated as Conjecture~\ref{conj:lvr-capture}.

\textbf{C3 (Quantitative envelope).} We characterize the protocol's operating envelope through Monte Carlo simulation across six scenarios (baseline, revenue-stop, mass-redemption, mass-dump, mixed-adversarial, organic-volume regimes) and sensitivity sweeps over the four free parameters. We identify Pareto frontiers between liquidity-pool longevity and floor compounding, and report stress trajectories under each adversarial composition. The simulation is validated against a Hardhat v3 invariant-test suite (Solidity \texttt{.t.sol} tests using \texttt{forge-std}-style assertions, run by Hardhat v3's EDR rather than by Foundry) that asserts floor monotonicity on the actual contracts; the two tracks must agree, with divergence treated as a paper-stopping bug.

\medskip
\noindent
\textbf{What we do not claim.} We do not claim spot-price monotonicity: the AMM spot can and will fall toward the floor in conditions of weak demand. We do not claim immunity to backing-stablecoin failure: the protocol holds a single deployer-chosen USD-pegged ERC-20, and its issuer's solvency is exogenous. We do not claim robustness to operator fraud at the revenue-deposit layer (the floor is preserved even at zero revenue, but its \emph{growth} depends on an operator continuing to route revenue; the threat-model boundary and real-world mitigations are catalogued in Sections~\ref{sec:protocol-threat-model} and~\ref{sec:lim-operator}). We do not claim end-to-end mechanized verification (we sketch the path and defer to follow-up). We do not predict token returns. We do not offer regulatory classification.

\subsection{Roadmap}

Section~\ref{sec:related-work} situates M\textsuperscript{2} in three literatures: TradFi capital returns and closed-end-fund redemption mechanics, DeFi tokenomic protocols (with attention to OHM \citep{OlympusDAO2021}, RAI \citep{Reflexer2021}, Frax \citep{Frax2021}, Liquity \citep{Liquity2021}, and MakerDAO \citep{Maker2019}), and formal-methods work on automated market makers and on-chain mechanism design. Section~\ref{sec:protocol} specifies the four contracts and introduces a threat model. Section~\ref{sec:formal-invariants} states and proves the floor-monotonicity, redemption-fairness, and integer-arithmetic redemption results. Section~\ref{sec:economic-analysis} formalizes the bank-run game and contrasts it with the Terra--Luna collapse \citep{LiuMakarovSchoar2023}. Section~\ref{sec:numerical-results} reports the simulation. Section~\ref{sec:comparison} provides a cross-protocol comparison matrix. Section~\ref{sec:limitations} catalogs limitations, open mathematical problems, and an academic regulatory framing. Section~\ref{sec:conclusion} closes.
