% ============================================================
\section{Economic Analysis}
\label{sec:economic-analysis}

The proofs of Section~\ref{sec:formal-invariants} establish a structural floor-monotonicity property: no protocol-defined operation can lower the floor. They do not yet address \emph{what an adversary chooses to do} when faced with the protocol. This section formalizes the adversarial decision problem as a redemption-versus-dump coordination game (a structural counterpoint to Diamond--Dybvig, whose multiple-equilibrium dynamics fail to obtain in M\textsuperscript{2}), characterizes the profit-maximizing composition of LP-dump and redemption strategies, derives the closed-form saturation point above which the dump-portion of any optimal strategy is bounded, contrasts the resulting dynamics with the Terra--Luna collapse \citep{LiuMakarovSchoar2023}, and analyzes the system's behavior under operator-revenue cessation through a closed-end-fund analog \citep{CherkesSagiStanton2009}. We also state the LP-exhaustion, MEV-leakage, and collect-fees-equilibrium results referenced in Section~\ref{sec:protocol}.

\subsection{The two exit paths}
\label{sec:econ-two-exits}

A holder of $N$ tokens, at state $\sigma = (\Tres, \Sup, \Lt, \Ls)$, has two protocol-defined exit channels. The \emph{redemption channel} burns the $N$ tokens and pays out $N \cdot \Floor$ stable from the treasury; by Theorem~\ref{thm:floor-monotonicity} Case~3, this preserves the floor exactly (and strictly raises it by a sub-unit residual under integer arithmetic; Lemma~\ref{lem:integer-redemption}). The \emph{LP-dump channel} routes the $N$ tokens through the AMM's sell side, where the hook deducts a $f_s = 3\%$ fee on input before the constant-product curve is applied. The holder may also mix the two strategies---redeem a fraction $1 - \alpha$ and dump a fraction $\alpha$, for any $\alpha \in [0, 1]$. The adversary's decision problem is to choose $\alpha$ to maximize total stable proceeds. We restrict attention throughout this subsection to \emph{simultaneous} strategies in which the attacker's dump and redemption occur in a single block, without an intervening \texttt{collectFees} realization; the strictly more permissive sequenced class is treated in the discussion following Theorem~\ref{thm:bank-run}.

Writing $M = \alpha N$ for the tokens routed to the LP, the LP payout function is
\begin{equation}
\pi_{\text{LP}}(M) \;=\; \Ls \;-\; \frac{\kInv}{\Lt + (1 - f_s) M},
\label{eq:lp-payout}
\end{equation}
which is strictly concave in $M$ on $M \geq 0$, with $\pi_{\text{LP}}(0) = 0$, $\pi_{\text{LP}}'(0) = (1 - f_s) \Ls/\Lt = (1 - f_s) \Spot$, and $\lim_{M \to \infty} \pi_{\text{LP}}(M) = \Ls$. The redemption payout is linear: $\pi_{\text{R}}(N - M) = (N - M) \Floor$. The total attacker yield as a function of the strategy $\alpha$ is
\begin{equation}
\Pi(\alpha; N, \sigma) \;=\; \pi_{\text{LP}}(\alpha N) \;+\; (1 - \alpha) N \Floor.
\label{eq:total-yield}
\end{equation}
$\Pi$ is concave in $\alpha$ on $[0, 1]$ (the LP term is concave; the redemption term is linear), so the maximum is attained either at a boundary or at the unique interior critical point.

\subsection{Saturation and the run-resistance theorem}
\label{sec:econ-bank-run}

Differentiating~\eqref{eq:total-yield} in $\alpha$ and setting the result to zero gives the interior optimum,
\begin{equation}
(\Lt + (1 - f_s) \alpha^* N)^2 \;=\; \frac{\kInv (1 - f_s)}{\Floor},
\label{eq:foc}
\end{equation}
which after rearrangement yields the saturation quantity
\begin{equation}
\boxed{\;A^* \;:=\; \alpha^* N \;=\; \frac{1}{1 - f_s}\left(\sqrt{\frac{\kInv (1 - f_s)}{\Floor}} \;-\; \Lt\right).\;}
\label{eq:saturation}
\end{equation}
The key structural fact is that $A^*$ depends only on the state $\sigma$, \emph{not on the adversary's holdings $N$.} The optimal dump quantity is a property of the AMM and the floor, not of the attacker's size.

\begin{theorem}[Composite-Strategy Bank Run with Saturation]
\label{thm:bank-run}
Within the simultaneous-strategy class of Section~\ref{sec:econ-two-exits}, at state $\sigma$, let $A^*$ be the saturation quantity~\eqref{eq:saturation} and let $\Pi^*(N; \sigma) = \max_{\alpha \in [0, 1]} \Pi(\alpha; N, \sigma)$ be the attacker's value function on holdings $N$. Then:
\begin{enumerate}
\setcounter{enumi}{-1}
\item \emph{(Pre-saturation regime.)} If $A^* \leq 0$---equivalently $(1 - f_s)\Spot \leq \Floor$, a near-launch or fee-suppressed-spot state in which the post-fee LP spot does not exceed the floor---the optimum is $\alpha^* = 0$ (pure redemption); pure redemption strictly dominates any positive dump under the asymmetric sell fee. The value is $\Pi^*(N) = N \Floor$.
\item \emph{(Pure-dump regime.)} If $0 < A^*$ and $N \leq A^*$, the optimum is $\alpha^* = 1$ (pure LP dump). The value is $\Pi^*(N) = \pi_{\text{LP}}(N) = \Ls - \kInv/(\Lt + (1 - f_s) N)$.
\item \emph{(Mixed regime.)} If $N > A^*$, the optimum is $\alpha^* = A^*/N \in (0, 1)$, with dump quantity exactly $A^*$ and redemption quantity $N - A^*$. The value is
\begin{equation}
\Pi^*(N) \;=\; (N - A^*) \Floor \;+\; \Big[\Ls - \sqrt{\kInv \Floor / (1 - f_s)}\Big].
\label{eq:mixed-value}
\end{equation}
\item \emph{(Bounded run premium.)} For any $N > A^*$, the run premium over pure redemption,
\begin{equation}
\Delta^* \;:=\; \Pi^*(N) - N \Floor \;=\; \Big[\Ls - \sqrt{\kInv \Floor / (1 - f_s)}\Big] - A^* \Floor,
\label{eq:run-premium}
\end{equation}
is a state-only constant, independent of $N$. The expression admits the equivalent closed forms
\begin{equation}
\Delta^* \;=\; \left(\sqrt{\Ls} - \sqrt{\Lt \Floor/(1-f_s)}\right)^2
\;=\; \Ls \cdot \left(1 - \sqrt{\Floor/((1-f_s)\Spot)}\right)^2,
\label{eq:run-premium-closed}
\end{equation}
which expose two structural facts: $\Delta^*$ vanishes whenever the post-fee LP spot $(1-f_s)\Spot$ approaches the floor $\Floor$, and the bound is structurally tight rather than $\Delta^* \leq \Ls$ in the worst case. At the canonical month-12 state, $\Floor/((1-f_s)\Spot) \approx 0.7637$ and $\Delta^*/\Ls \approx 1.59\%$ (not $100\%$).
\item \emph{(Asymptotic redemption.)} $\Pi^*(N) / N \to \Floor$ as $N \to \infty$. The marginal value of an additional held token, beyond what pure redemption returns, decays to zero.
\end{enumerate}
\end{theorem}

\begin{proof}
By concavity of $\Pi$ in $\alpha$, the unconstrained maximizer~\eqref{eq:foc} is the unique critical point. If $\alpha^* \geq 1$ (equivalently $A^* \geq N$), the constraint binds at $\alpha = 1$, giving regime~1. Otherwise the interior solution gives regime~2 with dump quantity $\alpha^* N = A^*$, a state-only constant. Substituting $\alpha^* = A^*/N$ into~\eqref{eq:total-yield} and simplifying using $\Lt + (1 - f_s) A^* = \sqrt{\kInv (1 - f_s)/\Floor}$ from~\eqref{eq:foc} yields~\eqref{eq:mixed-value}. The run premium~\eqref{eq:run-premium} is the constant tail in~\eqref{eq:mixed-value} after subtracting $N \Floor$. To obtain the closed form~\eqref{eq:run-premium-closed}, set $\beta = \sqrt{(1-f_s)/\Floor}$ and use $\kInv = \Lt \Ls$ to write $\sqrt{\kInv \Floor/(1-f_s)} = \sqrt{\Lt \Ls}/\beta$ and $A^* \Floor = (1/\beta^2)(\beta \sqrt{\Lt \Ls} - \Lt) = \sqrt{\Lt\Ls}/\beta - \Lt/\beta^2$, so
\[
\Delta^* \;=\; \Ls - \frac{2\sqrt{\Lt \Ls}}{\beta} + \frac{\Lt}{\beta^2} \;=\; \left(\sqrt{\Ls} - \sqrt{\Lt}/\beta\right)^2 \;=\; \left(\sqrt{\Ls} - \sqrt{\Lt\Floor/(1-f_s)}\right)^2.
\]
The second form in~\eqref{eq:run-premium-closed} follows by factoring $\sqrt{\Ls}$ and using $\Spot = \Ls/\Lt$. The asymptote in~(4) is immediate from $\Pi^*(N)/N = \Floor + \Delta^*/N \to \Floor$. $\qed$
\end{proof}

\paragraph{Structural interpretation of $\Delta^*$.} The closed form~\eqref{eq:run-premium-closed} shows that $\Delta^*$ is the LP's ``excess depth above the no-arbitrage curve'' at the asymmetric-fee-adjusted spot price. It scales with how far the post-fee spot $(1-f_s)\Spot$ exceeds the floor $\Floor$, not with $\Ls$ in the worst case: when the spot has been compressed by sustained selling so that $(1-f_s)\Spot \to \Floor$, the structural advantage of dumping over pure redemption vanishes entirely.

\paragraph{Sequenced strategies.} The simultaneous-strategy restriction of Theorem~\ref{thm:bank-run} excludes strategies in which the attacker interleaves \texttt{collectFees} between the dump and the redemption. In a sequenced strategy, the attacker dumps $A^*$ tokens, waits (or pays) for a \texttt{collectFees} call that realizes the token-side fees the attacker's own dump just deposited into $\Phit$, and only then redeems the remaining $N - A^*$ tokens against a now-higher floor. The marginal benefit over the simultaneous strategy is the floor increment $\Delta\Floor$ realized between dump and redemption, multiplied by the attacker's residual holdings $N - A^*$. At the canonical month-12 state, the dump of $A^* \approx 6.20 \cdot 10^7$ tokens deposits $f_s A^* \approx 1.860 \cdot 10^6$ tokens into $\Phit$, of which a fraction $1 - 0.0025$ (the caller bounty leaks the rest) is burned at the next \texttt{collectFees}; supply falls by $\approx 1.855 \cdot 10^6$ tokens, and the floor rises by $\Delta\Floor = \Tres/(\Sup - 1.855 \cdot 10^6) - \Tres/\Sup \approx \$6.698 \cdot 10^{-6}$ per token. The maximal sequenced premium, attained when the attacker initially holds the entire circulating supply $N = \Sup$, is $(N - A^*) \cdot \Delta\Floor \approx 6.047 \cdot 10^8 \cdot \$6.698 \cdot 10^{-6} \approx \$4{,}050$, an $18.9\%$ improvement on $\Delta^*$. Two structural observations: (i) the sequenced benefit \emph{is} a function of the attacker's holdings $N$, so the ``state-only constant'' claim of Theorem~\ref{thm:bank-run}(3) does not extend to the sequenced class; (ii) the per-held-token benefit is bounded above by $\Delta\Floor$ (a state-only quantity), so the simultaneous-class asymptote $\Pi^*(N)/N \to \Floor$ of part~(4) is replaced in the sequenced class by $\Pi^*_{\text{seq}}(N)/N \to \Floor + \Delta\Floor$---a strictly higher but still state-only-bounded asymptote. At canonical state this is $\Floor + 6.7 \cdot 10^{-6}$, a $0.28\%$ asymptotic premium per token. The qualitative ``no first-mover advantage'' content of Theorem~\ref{thm:redemption-fairness} is preserved, since the bound on the per-token gain remains independent of $N$. The closed-form supremum across the full sequenced strategy class---in which the attacker may interleave LP dumps, \texttt{collectFees} calls, and redemptions within or across blocks---is left as an open problem (Section~\ref{sec:lim-open-math}, P7); a full treatment requires modeling the equilibrium response of the \texttt{collectFees}-bounty payer and the v4 fee-realization timing dynamics.

\paragraph{Numerical illustration at the canonical month-12 state.} At the values produced by the deterministic 12-month projection of Section~\ref{sec:numerical-results}---$\Tres = \$1.6\text{M}$, $\Sup = 2 \cdot 10^9 / 3 \approx 6.667 \cdot 10^8$, $\Floor = \$0.0024$ exactly, $\Lt = 1.25 \cdot 10^9 / 3 \approx 4.167 \cdot 10^8$, $\Ls = \$1.35\text{M}$, $\kInv = \Lt \Ls = 5.625 \cdot 10^{14}$, $f_s = 0.03$---equation~\eqref{eq:saturation} gives
\begin{equation*}
\sqrt{\tfrac{\kInv (1-f_s)}{\Floor}} = \sqrt{2.273\overline{4} \cdot 10^{17}} \approx 4.76806 \cdot 10^8, \qquad A^* \approx 6.1999 \cdot 10^7 \text{ tokens},
\end{equation*}
which is about $9.30\%$ of the circulating supply. Equation~\eqref{eq:run-premium} then evaluates as
\begin{equation*}
\Delta^* = \underbrace{\$1{,}350{,}000}_{\Ls} - \underbrace{\sqrt{\tfrac{\kInv \Floor}{1-f_s}}}_{\approx \$1{,}179{,}725.64} - \underbrace{A^* \Floor}_{\approx \$148{,}797.80} \approx \$21{,}476.56.
\end{equation*}
The closed-form value, computed in 60-digit decimal arithmetic, is $\Delta^* = \$21{,}476.5621\ldots$; the figures in the paper are rounded to the nearest cent. Even an adversary with the entire circulating supply $N = \Sup$ can extract at most $N \Floor + \Delta^* \approx \$1{,}621{,}476.56$ from the system---this is the treasury balance plus a residual constant bounded above by $\Ls$.

\paragraph{Pure-strategy crossover.} A naive pure-strategy analysis would equate the two pure-strategy yields $\pi_{\text{LP}}(N) = N \Floor$ to find a crossover $N^{\text{cross}}$ where pure dump and pure redemption yield the same proceeds; numerically at the canonical month-12 state, $N^{\text{cross}} \approx 1.33 \cdot 10^8$. Theorem~\ref{thm:bank-run} subsumes this: the saturated mixed strategy of regime~(2) yields more than either pure strategy whenever $N > A^*$, so the pure-strategy crossover is informationally inferior to~\eqref{eq:run-premium} as a characterization of the attacker's optimal yield.

\paragraph{Diamond--Dybvig contrast.} The classical \citet{DiamondDybvig1983} model produces multiple-equilibrium bank-run dynamics because the bank's reserves are finite and patient depositors strictly lose if impatient depositors redeem first. In M\textsuperscript{2}, by Theorem~\ref{thm:redemption-fairness}, later redeemers weakly dominate earlier redeemers in floor terms; by Theorem~\ref{thm:bank-run}(3), the total adversarial premium over redemption is bounded by a state-only constant; and by Theorem~\ref{thm:floor-monotonicity}, no operation in $\mathrm{Ops}$ reduces the floor. The strategic-complementarity channel of \citet{ChenGoldsteinJiang2010} (early redeemers extract value from later ones) is structurally absent. The M\textsuperscript{2} ``run'' is a single-equilibrium game in which the rational strategy converges to pure redemption as $N$ grows, and the system's terminal state under a complete-redemption attack is the same as its terminal state under no attack at all: the LP retains its $\kInv$, the treasury drains in lockstep with supply burn, and the per-token floor is preserved.

\subsection{Disanalogy with the Terra--Luna collapse}
\label{sec:econ-terra}

The Terra--Luna collapse \citep{LiuMakarovSchoar2023,Briola2023} is the standard cautionary tale of an algorithmic-stablecoin system that entered a reflexive death spiral under coordinated redemption pressure. The mechanism: UST redemption minted LUNA at the prevailing LUNA price, so a coordinated UST sell increased LUNA supply, lowering LUNA price, which further raised the LUNA quantity minted per UST burned, and so on. The endogenous-collateral structure produced a positive feedback loop in which redemption amplified its own pressure.

The M\textsuperscript{2} disanalogy is structural along three axes:
\begin{enumerate}
\item \emph{Collateral exogeneity.} The M\textsuperscript{2} treasury holds a single deployer-chosen USD-pegged ERC-20 (e.g.\ USDC, DAI). The protocol does not mint the backing stable. There is no endogenous-collateral feedback channel of the Terra--LUNA kind because the backing asset's supply and price are not protocol-determined.
\item \emph{One-way treasury inflow.} Redemption removes stable from the treasury only in lockstep with burning the redeemed tokens. The per-token claim $\Floor = \Tres/\Sup$ is therefore invariant across redemption events, by Lemma~\ref{lem:integer-redemption}. In Terra--LUNA, redemption changed both legs (UST supply down, LUNA supply up) by ratios that did not preserve any analogous invariant.
\item \emph{No pegging mechanism.} M\textsuperscript{2} is not a stablecoin and has no peg target. The AMM spot price floats; only the floor is invariant-protected. Terra--LUNA's collapse depended on the loss of confidence in a peg target; M\textsuperscript{2} has no target to lose.
\end{enumerate}
The closest TradFi analog of M\textsuperscript{2} is a closed-end fund holding U.S. dollars in custody with continuous NAV redemption \citep{LeeShleiferThaler1991,CherkesSagiStanton2009}. The closest \emph{negative} analog is Terra--LUNA. The crucial design choice that places M\textsuperscript{2} in the first category and not the second is the exogeneity of the backing asset.

\subsection{Operator-revenue cessation and the CEF analog}
\label{sec:econ-operator}

The growth of the floor depends on the operator's continued routing of business revenue. If the operator stops depositing (whether by choice, bankruptcy, or third-party disruption), revenue inflow becomes zero. We characterize the system's degradation under this regime through a closed-end-fund analog.

\begin{theorem}[Spot--Floor Convergence under Zero Revenue]
\label{thm:spot-floor-convergence}
Suppose the operator deposits no revenue from time $t_0$ onward. Let $D(t) := \Spot(t) - \Floor(t)$. Then:
\begin{enumerate}
\item \emph{(Floor stickiness.)} $\Floor(t)$ is non-decreasing in $t$ (Theorem~\ref{thm:floor-monotonicity}). Strict increases occur only on \texttt{collectFees} invocations realizing organic-flow fees.
\item \emph{(Spot floor via arbitrage.)} Under any positive-probability arbitrageur path---arbitrageurs are available to buy on the LP whenever $\Spot < \Floor$---we have $\Spot(t) \geq \Floor(t)$ for all $t \geq t_0$. Equivalently, $D(t) \geq 0$.
\item \emph{(Convergence under net-sell pressure.)} Suppose that after $t_0$ the cumulative non-arbitrage sell volume strictly exceeds the cumulative non-arbitrage buy volume in expectation, while arbitrageurs remain available to buy whenever $\Spot < \Floor$ as in~(2). Then $\Spot(t)$ is non-increasing in expectation outside arbitrage events (non-arbitrage sells push it down; arbitrage entry prevents it from settling below the floor), $\Floor(t)$ is non-decreasing, and $D(t)$ converges to a limit bounded above by the arbitrage threshold $f_b \cdot \Floor \approx 10$ basis points of $\Floor$ (the minimum gap at which a one-dollar-sized arbitrage round-trip is profitable; smaller trades face proportionally larger relative gas costs).
\end{enumerate}
\end{theorem}

\begin{proof}[Proof sketch]
(1) Direct from Theorem~\ref{thm:floor-monotonicity}: in the zero-revenue regime, only Cases~3, 4, 5, 6, 7 of the operation set are exercised, and none lowers the floor. (2) Suppose for contradiction $\Spot(t) < \Floor(t)$. An arbitrageur can buy on the LP at $\Spot$ (paying the 0.10\% buy fee), redeem against the treasury at $\Floor$, and net a profit of $(\Floor - \Spot)/\Spot - 0.001$ per dollar deployed---positive whenever the gap exceeds 10 basis points. The buy raises $\Spot$ and the redemption preserves $\Floor$; the gap is closed by the assumed positive-probability path. (3) Non-arbitrage sells lower $\Spot$ along the AMM curve; the floor either stays flat or rises on \texttt{collectFees}. Whenever spot would drop more than $f_b \cdot \Floor$ below floor, the arbitrage of~(2) is triggered (an arbitrageur buys back on the LP and redeems against the treasury), pinning spot from below at $\Floor (1 - f_b)$ up to the buy-fee threshold. The two quantities approach each other monotonically, with $D(t)$ converging to a limit bounded above by $f_b \cdot \Floor$ (the per-dollar break-even threshold of the arbitrage round-trip). The terminal regime is reached either when the LP exhausts its stable reserve or when the arbitrage rounds the gap to within the $f_b$ threshold. $\qed$
\end{proof}

In words: when revenue stops, M\textsuperscript{2} degrades to a CEF whose NAV is monotone-nondecreasing in time (from any residual \texttt{collectFees} activity) and whose secondary market converges to NAV. This is strictly stronger than any TradFi CEF, where the persistent discount-to-NAV documented by \citet{LeeShleiferThaler1991} and \citet{Pontiff1996} reflects the absence of a contractual NAV-redemption mechanism. The protocol's invariants are silent on operator \emph{fraud} (revenue collected but routed elsewhere); the threat-model boundary appears in Section~\ref{sec:protocol-threat-model} and the real-world mitigations in Section~\ref{sec:lim-operator}.

\subsection{LP exhaustion asymptotics}
\label{sec:econ-lp}

Under deterministic monthly buy-and-burn of constant size $B$ stable, the LP's stable reserve grows linearly while its token reserve decays hyperbolically.

\begin{theorem}[LP Half-Life]
\label{thm:lp-half-life}
Let $L_{s,0}, L_{t,0}$ be the genesis LP reserves and $\kInv = L_{t,0} L_{s,0}$ the constant-product invariant. Assume deterministic monthly buy size $B$ stable into the LP for $n$ months (ignoring intervening organic flow). Then $\Ls(n) = L_{s,0} + nB$, $\Lt(n) = \kInv/(L_{s,0} + nB)$, and the token-side half-life---the smallest $n_{1/2}$ such that $\Lt(n_{1/2}) \leq L_{t,0}/2$---is
\begin{equation}
n_{1/2} \;=\; L_{s,0} / B.
\label{eq:lp-half-life}
\end{equation}
\end{theorem}

\begin{proof}
The hook's buy-and-burn execution preserves $\kInv$ (the asymmetric 0.10\% buy fee is folded into $\Phis$ and realized only at \texttt{collectFees}; on the swap itself, $\kInv$ is preserved). Each monthly buy adds $B$ stable to the active reserves, so $\Ls(n) = L_{s,0} + nB$. From $\kInv = \Lt(n) \Ls(n)$, $\Lt(n) = \kInv/\Ls(n) = L_{t,0} L_{s,0}/(L_{s,0} + nB)$. Setting $\Lt(n_{1/2}) = L_{t,0}/2$ gives $L_{s,0}/(L_{s,0} + n_{1/2} B) = 1/2$, i.e., $n_{1/2} = L_{s,0}/B$. $\qed$
\end{proof}

At the canonical genesis ($L_{s,0} = \$750{,}000$) and $B = \$50{,}000$/month (the 50\% buy-and-burn slice of \$100k/month revenue), $n_{1/2} = 15$ months. The system's transition from ``tradable token'' to ``redemption-dominant'' regime is a deterministic function of the revenue rate and is plotted in Figure~\ref{fig:revenue-sweep} (right axis: $n_{1/2}(R)$ over the revenue sweep).

\subsection{Collect-fees calling equilibrium}
\label{sec:econ-collect}

The \texttt{collectFees} function is permissionless and pays a 0.25\%-per-side bounty to the caller. The calling cadence is determined by a deterministic competitive race among potential callers.

\begin{theorem}[Calling Equilibrium under Atomless Competition]
\label{thm:collect-equilibrium}
Let $\beta$ be the steady-state per-unit-time rate of fee accumulation in the v4 accumulator (a function of swap volume, the asymmetric fee, and the position's liquidity share), and $g$ the gas-plus-search cost of a \texttt{collectFees} call. Assume atomless risk-neutral competition among potential callers: infinitely many would-be callers each willing to call at the first profitable moment. Then the equilibrium inter-call interval $\Delta t^*$ satisfies the Bertrand-style break-even condition
\begin{equation}
0.0025 \cdot \beta \cdot \Delta t^* \;=\; g,
\qquad
\text{i.e.,} \qquad
\Delta t^* \;=\; \frac{g}{0.0025 \,\beta}.
\label{eq:collect-eq}
\end{equation}
For $\beta$ growing in swap volume, $\Delta t^*$ shrinks proportionally; in low-volume regimes, $\Delta t^*$ may exceed the protocol's monthly tick, in which case the protocol routes its own buy-and-burn through a fee realization on the same transaction (a path that does not require the bounty).
\end{theorem}

\begin{proof}[Proof sketch]
A caller who waits an interval $\Delta t$ earns the deterministically accrued bounty $0.0025 \beta \Delta t$ and pays the fixed cost $g$. Under atomless competition, no caller can wait longer than the first $\Delta t$ at which the bounty covers $g$ without being preempted by a competitor; no caller will call earlier, since doing so yields a strict loss. The standard Bertrand-style indifference under competitive entry pins the equilibrium at the break-even point~\eqref{eq:collect-eq}, with no intertemporal discounting because the equilibrium interval is short relative to the deployer's time horizon. $\qed$
\end{proof}

\paragraph{Monopoly deviation.} The atomless-competition assumption is the load-bearing piece of the equilibrium. Under monopoly---a single sophisticated keeper who faces no competitive preemption---the equilibrium $\Delta t$ is strictly longer and reflects the keeper's outside option (e.g., capital cost or alternative MEV opportunities). The protocol does not depend on monopoly being absent: the permissionless calling interface remains open to all entrants, and any monopoly rent is bounded above by the gap between the keeper's outside option and the gas cost.

The economic content is that the bounty rate is a knob controlling the trade-off between fee-realization latency (low bounty $\Rightarrow$ long $\Delta t^*$) and value leakage to extractors (high bounty $\Rightarrow$ more value lost per call). The 0.25\%-per-side rate is locked at genesis (Section~\ref{sec:protocol-collect}); we do not optimize over it.

\subsection{MEV leakage on protocol buy-and-burn}
\label{sec:econ-mev}

Protocol buy-and-burn is in expectation predictable: a monthly cadence with a buy direction. Naive execution into a public mempool is sandwichable. The hook's mitigations (private orderflow, random delay, TWAP) bound the residual leakage.

\begin{theorem}[MEV Leakage Upper Bound]
\label{thm:mev-bound}
Let $p \in [0, 1]$ be the probability that a buy-and-burn transaction is included via a private (sealed) route, $N_{\text{TWAP}}$ the TWAP granularity, and $B$ the monthly buy size in stable. Let $\varepsilon_{\text{pub}}(M, \Ls)$ denote the public-mempool sandwich efficiency for a swap of size $M$ against stable reserves $\Ls$, satisfying $\varepsilon_{\text{pub}}(M, \Ls) = O(M/\Ls)$ in the small-impact regime. Then the expected MEV leakage on the monthly buy satisfies
\begin{equation}
\mathbb{E}[\mathrm{MEV}] \;\leq\; (1 - p) \cdot \varepsilon_{\text{pub}}(B/N_{\text{TWAP}}, \Ls) \cdot B \;+\; p \cdot \varepsilon_{\text{priv}} \cdot B,
\label{eq:mev-bound}
\end{equation}
where $\varepsilon_{\text{priv}}$ is the (small) private-mempool sandwich efficiency under builder-collusion risk. In particular, for fixed $p$, $\mathbb{E}[\mathrm{MEV}]/B \to p \varepsilon_{\text{priv}}$ as $N_{\text{TWAP}} \to \infty$.
\end{theorem}

\begin{proof}[Proof sketch]
With probability $p$ the transaction is in the private channel where only builder-collusion-level adversaries can sandwich, with efficiency $\varepsilon_{\text{priv}}$; with probability $1 - p$ it is in the public mempool where the searcher can sandwich the swap, with efficiency $\varepsilon_{\text{pub}}$ in the swap's quadratic-impact order. Splitting the monthly buy into $N_{\text{TWAP}}$ equal parts reduces each sub-buy's impact to $B/N_{\text{TWAP}}$, on which the sandwich extracts $\varepsilon_{\text{pub}}(B/N_{\text{TWAP}}, \Ls) \cdot B/N_{\text{TWAP}}$, aggregated over $N_{\text{TWAP}}$ sub-buys; the linearity of expectation gives the first term in~\eqref{eq:mev-bound}. The private leg contributes the second term. $\qed$
\end{proof}

At the design's canonical parameters ($B = \$50\text{k}/\text{month}$, $\Ls \in [\$0.75\text{M}, \$2\text{M}]$ across the first 36 months, $p \approx 0.95$ on Ethereum mainnet via Flashbots Protect, $N_{\text{TWAP}} = 8$), equation~\eqref{eq:mev-bound} predicts $\mathbb{E}[\mathrm{MEV}]/B \lesssim 0.5\%$, well under a $1\%$-of-revenue target. Multi-block MEV under builder collusion is explicitly out of scope (Section~\ref{sec:protocol-threat-model}, Section~\ref{sec:limitations}).
